---
title: "Karl Lagerfeld: Related Products Experiment"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

```{r global, include=T, echo = FALSE, message = FALSE}
### Lib.
library(tidyverse)
library(bigrquery)
library(data.table)
library(flexdashboard)
library(highcharter)
library(openxlsx)

c10 <- fread('elencoC10Karl.csv')
results <- fread('results.csv')
ourC10 <- read.xlsx('KL_Related.xlsx', startRow = 3)
theirC10 <- read.xlsx('KL_Export.xlsx', startRow = 3)
```

Row 
-----------------------------------------------------------------------

### CTR % Pre-Experiment 

```{r}
results %>% 
  mutate(C10Master = str_to_upper(C10Master),
         Date = as.Date(as.character(Date), format = '%Y%m%d')) %>% 
  filter(Date < as.Date('2018-05-10'), Date > as.Date('2018-04-10')) %>%
  summarise(CTR = sum(click, na.rm = TRUE) / sum(impressions)) * 100 -> CTRPre0  

valueBox(paste0(round(CTRPre0$CTR, 2), ' %'), icon = 'fa-pencil') 
```

### CTR % Post-Experiment 

```{r}
results %>% 
  mutate(C10Master = str_to_upper(C10Master),
         Date = as.Date(as.character(Date), format = '%Y%m%d')) %>% 
  filter(Date >= as.Date('2018-05-10')) %>%
  summarise(CTR = sum(click, na.rm = TRUE) / sum(impressions)) * 100 -> CTRPost0  

valueBox(paste0(round(CTRPost0$CTR, 2), ' %'), icon = 'fa-pencil') 
```

### Changes % in CTR %

```{r}
DeltaCTR0 <- CTRPost0$CTR / CTRPre0$CTR - 1
DeltaCTRVerbose0 <- paste0(round(DeltaCTR0*100, 2), ' %')

valueBox(paste0(round(DeltaCTR0*100, 2), ' %'), 
         icon = 'fa-comments',
         color = ifelse(DeltaCTR0 < 0, "warning", "success")) 
```


Row
-----------------------------------------------------------------------

### CTR % of All Related Items
```{r}
results %>% 
  mutate(C10Master = str_to_upper(C10Master),
         Date = as.Date(as.character(Date), format = '%Y%m%d')) %>%
  group_by(Date) %>% 
  summarise(CTR = sum(click, na.rm = TRUE) / sum(impressions)) %>% 
  mutate(isPre = ifelse(Date <= as.Date('2018-05-09'), 'Pre Experiment', 'Post Experiment')) %>%
  hchart("line", hcaes(x = Date, y = round(CTR*100, 2), group = isPre)) %>%
  hc_add_theme(hc_theme_smpl()) %>% 
  hc_legend(align = "left", verticalAlign = "top",
            layout = "vertical", x = 0, y = 100) %>%
  hc_tooltip(crosshairs = TRUE, backgroundColor = "#FCFFC5",
             shared = TRUE, borderWidth = 5) %>%
  hc_yAxis(title = list(text = 'CTR %')) %>%
  hc_exporting(
    enabled = TRUE
  )
```

### Explanation

Time Series of **Click Through Rate** % of **all C10**, segmented for Pre-Post Experiment time dimension.<br><br>

**Blue** line represents overall CTR % **pre-experiment**: it shows a **steady trend**, around average **0.2%**.<br><br>

**Red** line represents overall CTR % **post-experiment**, with a **strong uplift** thanks to both improvements in modified C10 and newly added C10.<br><br>

We should expect an average increase of **+`r DeltaCTRVerbose0`** using our method, keeping constant all other external variables.<br><br><br>

Row 
-----------------------------------------------------------------------

### CTR % Pre-Experiment (Manual vs Data-Driven)

```{r}
results %>% 
  mutate(C10Master = str_to_upper(C10Master),
         Date = as.Date(as.character(Date), format = '%Y%m%d')) %>% 
  inner_join(c10, by = c('C10Master' = 'Master')) %>% 
  filter(Date < as.Date('2018-05-10'), Date > as.Date('2018-04-10')) %>%
  summarise(CTR = sum(click, na.rm = TRUE) / sum(impressions)) * 100 -> CTRPre  

valueBox(paste0(round(CTRPre$CTR, 2), ' %'), icon = 'fa-pencil') 
```

### CTR % Post-Experiment (Manual vs Data-Driven)

```{r}
results %>% 
  mutate(C10Master = str_to_upper(C10Master),
         Date = as.Date(as.character(Date), format = '%Y%m%d')) %>% 
  inner_join(c10, by = c('C10Master' = 'Master')) %>% 
  filter(Date >= as.Date('2018-05-10')) %>%
  summarise(CTR = sum(click, na.rm = TRUE) / sum(impressions)) * 100 -> CTRPost  

valueBox(paste0(round(CTRPost$CTR, 2), ' %'), icon = 'fa-pencil') 
```

### Changes % in CTR %

```{r}
DeltaCTR <- CTRPost$CTR / CTRPre$CTR - 1
DeltaCTRVerbose <- paste0(round(DeltaCTR*100, 2), ' %')

valueBox(paste0(round(DeltaCTR*100, 2), ' %'), 
         icon = 'fa-comments',
         color = ifelse(DeltaCTR < 0, "warning", "success")) 
```

Row
-----------------------------------------------------------------------

### CTR % of modified Products by "Data Driven" Rules 

```{r}
results %>% 
  mutate(C10Master = str_to_upper(C10Master),
         Date = as.Date(as.character(Date), format = '%Y%m%d')) %>% 
  inner_join(c10, by = c('C10Master' = 'Master')) %>% 
  group_by(Date) %>% 
  summarise(CTR = sum(click, na.rm = TRUE) / sum(impressions)) %>% 
  mutate(isPre = ifelse(Date <= as.Date('2018-05-09'), 'Manual', 'Data-Driven')) %>%
  hchart("line", hcaes(x = Date, y = round(CTR*100, 2), group = isPre)) %>%
  hc_add_theme(hc_theme_smpl()) %>% 
  hc_legend(align = "left", verticalAlign = "top",
            layout = "vertical", x = 0, y = 100) %>%
  hc_tooltip(crosshairs = TRUE, backgroundColor = "#FCFFC5",
             shared = TRUE, borderWidth = 5) %>%
  hc_yAxis(title = list(text = 'CTR %')) %>%
  hc_exporting(
    enabled = TRUE
  )
```

### Explanation

It takes into account only C10 that have been **modified by Data-Driven rules** and that were previously been enriched in a manually fashion.<br><br>

They're **47 products**, belonging to the short tail of most interacted items.<br><br>

Comparison has been made on a 30days window, pre and post experiment (launch on May 10th). <br><br>

**Data-Driven** rules are currently outperforming manual rules by **+ `r DeltaCTRVerbose`**, suggesting better performance having been carry over by our algorithms.<br><br>


Row
-----------------------------------------------------------------------

### CTR % Pre-Experiment (Platform vs Data-Driven) 

```{r}
results %>% 
  mutate(C10Master = str_to_upper(C10Master),
         Date = as.Date(as.character(Date), format = '%Y%m%d')) %>% 
  inner_join(ourC10 %>% left_join(theirC10, by = c('Master' = 'Master')) %>% filter(is.na(Related.1.y)) %>% distinct(Master), by = c('C10Master' = 'Master')) %>%
  filter(Date < as.Date('2018-05-10'), Date > as.Date('2018-04-10')) %>%
  summarise(CTR = sum(click, na.rm = TRUE) / sum(impressions)) * 100 -> CTRPre2  

valueBox(paste0(round(CTRPre2$CTR, 2), ' %'), icon = 'fa-pencil') 
```

### CTR % Post-Experiment (Platform vs Data-Driven)

```{r}
results %>% 
  mutate(C10Master = str_to_upper(C10Master),
         Date = as.Date(as.character(Date), format = '%Y%m%d')) %>% 
  inner_join(ourC10 %>% left_join(theirC10, by = c('Master' = 'Master')) %>% filter(is.na(Related.1.y)) %>% distinct(Master), by = c('C10Master' = 'Master')) %>%
  filter(Date >= as.Date('2018-05-10')) %>%
  summarise(CTR = sum(click, na.rm = TRUE) / sum(impressions)) * 100 -> CTRPost2  

valueBox(paste0(round(CTRPost2$CTR, 2), ' %'), icon = 'fa-pencil') 
```

### Changes % in CTR %

```{r}
DeltaCTR2 <- CTRPost2$CTR / CTRPre2$CTR - 1
DeltaCTRVerbose2 <- paste0(round(DeltaCTR2*100, 2), ' %')

valueBox(paste0(round(DeltaCTR2*100, 2), ' %'), 
         icon = 'fa-comments',
         color = ifelse(DeltaCTR2 < 0, "warning", "success")) 
```

Row 
-----------------------------------------------------------------------

### CTR % of Newly Added Products by "Data Driven" Rules

```{r}
results %>% 
  mutate(C10Master = str_to_upper(C10Master),
         Date = as.Date(as.character(Date), format = '%Y%m%d')) %>% 
  inner_join(ourC10 %>% left_join(theirC10, by = c('Master' = 'Master')) %>% filter(is.na(Related.1.y)) %>% distinct(Master), by = c('C10Master' = 'Master')) %>% 
  group_by(Date) %>% 
  summarise(CTR = sum(click, na.rm = TRUE) / sum(impressions)) %>% 
  mutate(isPre = ifelse(Date <= as.Date('2018-05-09'), 'Platform', 'Data-Driven')) %>%
  hchart("line", hcaes(x = Date, y = round(CTR*100, 2), group = isPre)) %>%
  hc_add_theme(hc_theme_smpl()) %>% 
  hc_legend(align = "left", verticalAlign = "top",
            layout = "vertical", x = 0, y = 100) %>%
  hc_tooltip(crosshairs = TRUE, backgroundColor = "#FCFFC5",
             shared = TRUE, borderWidth = 5) %>%
  hc_yAxis(title = list(text = 'CTR %')) %>%
  hc_exporting(
    enabled = TRUE
  )
```


### Explanation

It takes into account only newly enriched C10 **by Data-Driven rules** that were previously been treated with **platform rules** (random rotation of products within the same category). <br><br>

Our algorithm was been able to find out more than **70 items**, from the most interacted items cluster, with at least 2 related items.<br><br>

Comparison has been made on a 30days window, pre and post experiment (launch on May 10th). <br><br>

**Data-Driven** rules are currently outperforming platform rules by a **+ `r DeltaCTRVerbose2`**, suggesting much better performance having been carry over by our algorithms.<br><br>

